---
title: "KidStats Report"
output: word_document
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pander)
```

**Case ID: `r input$caseid`**

**Analyst: `r input$analyst`**

Generated by KidStats v`r ks_version()` on `r Sys.Date()`
<br>
https://kyra-stull.shinyapps.io/kidstats/


----

## Results

- Point Estimation: **`r round(analysis()$post$xmean, digits = 2)`**
- Lower 95% Prediction Interval: **`r round(analysis()$post$xlo, digits = 2)`**
- Upper 95% Prediction Interval: **`r round(analysis()$post$xhi, digits = 2)`**

```{r echo=FALSE, message=FALSE, warning=FALSE}
yada::plot_x_posterior(analysis()$post)
```

## Input

- Sample Population: **`r input$refsamp`**
- Known Age: **`r input$xknown`**
<!-- - Sample Sex: **`r input$sexsamp`** -->
<!-- - Age Prior: **`r input$ageprior`** -->

<br>

#### Input measurements

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#input_list <- data.frame(Variable=names(case_data), Value=unname(unlist(case_data[1,])))
input_list <- data.frame(Variable = names(case_data()), Value = unname(unlist(case_data()[1,])))
pandoc.table(input_list, justify = 'centre')
```